### 2013-09-26 manuscripts/reply/reply.tex
Incorporating Charles' `cwlnote`s into the reply.

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Recently, \citet{Oaks2012} presented a simulation-based
    assessment of the approximate Bayesian phylogeographical model choice
    method implemented in \msb, and found the method to lack robustness and
    power to detect temporal variation in divergences that are randomly
    distributed over relatively broad periods of evolutionary history.
    They conclude that a likely mechanism behind the bias toward models with
    few divergence events is the small marginal likelihoods of models with more
    divergence time parameters due to the integration over vast parameter space
    imposed by broad uniform priors characterized by low likelihood and high
    prior density.
    This phenomenon is often referred to as Lindley's paradox
    \citep{Lindley1957}.  \citet{Hickerson2013} have responded to this work,
    criticising the priors used by \citet{Oaks2012} and presenting an
    approximate Bayesian model-averaging approach that uses narrow, empirically
    informed uniform priors.
    \citet{Hickerson2013} conclude this approach circumvents the issues
    revealed by \citet{Oaks2012} and yields robust inference of divergence
    models.
    Furthermore, they argue that the biases revealed by \citet{Oaks2012} are
    inherent to the inefficient rejection algorithm implemented in \msb, rather
    than a result of Lindley's paradox.
    Here we show that \cwlnote{their}{the} methodology \cwlnote{suffered}{of \citet{Hickerson2013}} suffers from a fundamental error that
    renders some of their results invalid and the remainder difficult to
    interpret.
    Furthermore, we demonstrate how \cwlnote{their}{the} approach \cwlnote{}{of \citet{Hickerson2013}} still suffers from a bias
    toward models with \cwlnote{lesser}{less} parameter space, which manifests in a dangerously
    strong tendency to sample predominantly from models that exclude the true
    values of the model's parameters.
    Our results suggest that their model-averaged results are dominated by
    models that likely exclude at least some of the true divergence times
    across the 22 pairs of Philippine vertebrates, which adds to the
    difficulty in interpreting their results.
    We also show that in addition to this dangerous behavior, the approach of
    \citet{Hickerson2013} is still strongly biased toward inferring
    simultaneous divergences even when the true divergences are randomly
    distributed over millions of generations.
    Our results, coupled with those of \citet{Oaks2012}, strongly suggest that
    Lindley's paradox is a primary cause of the bias of \msb toward models with
    lesser parameter space.
    We discuss ways to mitigate this bias without resorting to adding an
    additional dimension of model choice to the model or using dangerous
    empirically informed uniform priors.

@@

\highLight{The goal of this paper needs to be to highlight the major differences of opinion on how ABC can be used in comparative phylogeography and how these changes to msbayes can be made that will improve the inference in the future. We should avoid nit-picking the Hickerson paper and try to stay positive.}

@@

Regarding the mechanism behind the poor behavior of the method,
\citet{Oaks2012} suggest the primary cause is likely the low marginal
likelihoods of parameter-rich models integrated over vast parameter space with
low probability of producing the data, yet relatively high prior density
\citep[this is often referred to as Lindley's paradox;][]{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest it is intrinsic to \msb, concluding the method's rejection algorithm is inefficient and will be
increasingly biased as the overall space of the model increases, either as a
function of the number of taxon pairs or the width of the uniform priors on
nuisance parameters.
\citet{Hickerson2013} support their position by giving a probabilistic argument that focuses on
only one of the three prior models used by \citet{Oaks2012}.
We show that the empirical Bayesian approach used by \citet{Hickerson2013} is based on questionable assumptions, and does not explain the
bias of the method found in many of the analyses of \citet{Oaks2012}. 
Furthermore, we show that the model-averaging approach suggested by \citet{Hickerson2013} does not correct the bias towards small priors and we present results of additional analyses, which strongly suggest that
Lindley's paradox is playing a large role in the poor behavior of \msb.

@@

%To mitigate the bias, \citet{Oaks2012} suggest that more cogent
%prior probability distributions on divergence models and nuisance parameters
%could reduce the effect of Lindley's paradox.
%They also layout a set of simulation-based procedures for determining power,
%accuracy, and robustness of the method given a dataset, and recommend any
%application of \msb should be accompanied by such procedures, especially if any
%biological conclusions are drawn from the results.
%\citet{Hickerson2013} present an approximate Bayesian model-averaging approach
%for accommodating uncertainty in selecting among empirically guided priors, and
%champion the method as a means of avoiding the pitfalls raised by
%\citet{Oaks2012}.
%Unfortunately, we show that fundamental errors in this approach render some of
%their results invalid and leave the remaining results difficult to interpret.
%Furthermore, we follow the advice of \citet{Oaks2012} and present
%simulation-based assessments of Hickerson et al.'s (\citeyear{Hickerson2013})
%approach.
%Our results demonstrate that the new method of \citet{Hickerson2013} is biased and dangerous.  The approach
%merely provides another means by which the model can ``escape'' large parameter
%space, and bias toward smaller models remains.
%This manifestation of the bias can be dangerous and often excludes the true
%parameter space due to the use of narrow uniform priors.
%Furthermore we discuss the potential theoretical and practical problems of
%empirical Bayesian model choice, which is used and encouraged by
%\citet{Hickerson2013} without any mention of its potential complications.

%It may be important to point out the error made in their paper, but it can also be nit-picky, it depends on how the error impacts the overall message of our response. 
%We should strive to keep the response short and directed at the big picture items. If there is a way to still point out the error, then maybe some of this section should be used
\iffalse
\section*{An error in Hickerson et al.'s re-analysis of the Philippines data}
\citet{Hickerson2013} re-analyzed the dataset of \citet{Oaks2012} using a
model-averaging approach, where they placed a discrete uniform prior over eight
different prior models (see Table 1 of \citet{Hickerson2013}).
In our initial attempts to explore the behavior of this approach, we found
a fundamental error in the methodology of \citet{Hickerson2013}:
their model mixes different time units.

@@

\cwlnote{}{This part seems important, but not related to the error in units discussed above}
Another important characteristic of the approach used by \citet{Hickerson2013}
that makes their results difficult to interpret in addition to this error is
their use of narrow, empirically guided uniform priors in an approximate
Bayesian model choice framework.
We discuss the dangers of this approach in the next section, and show how the
results of \citet{Hickerson2013} likely exclude true values of the model's
parameters.
\fi

@@

\iffalse
\section*{The dangers of empirical Bayesian model choice}

\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected''. 
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They detail that the limitation in using uniform prior distributions in \msb
necessitates awkward broad priors to avoid excluding the truth, \textit{a priori}.
What \citet{Hickerson2013} really mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing both the
prior sensitivity of the method and determining the power of \msb under
real-world conditions with highly informative priors.  
\citet{Oaks2012} discuss
the potential dangers of taking an empirical Bayesian approach to model choice
(see the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}), and we expand on this here by exploring both the theoretical
and practical implications of using empirically informed priors for Bayesian
model choice.
\fi

\section*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}

Bayesian inference is a rational method of inductive learning in which Bayes'
rule is used to update our beliefs about a model as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values, we can define a prior distribution for all $\theta \in
\allParameterValues$ such that $p(\theta)$ describes our belief \cwlnote{}{is belief the right term in this section? Would probability or likelihood be better?}
 that any given
\myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \in
\allParameterValues$ and $\alignment{}{} \in \allDatasets$ such that
$p(\alignment{}{} | \theta)$ measures our belief that any dataset \alignment{}{}
will be generated by any model state \myTheta{}.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given 
    \myTheta{})p(\myTheta{})}{p(\alignment{i}{})},
    \label{eq:bayesrule}
\end{equation}
where
\begin{equation}
    p(\alignment{i}{}) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{})p(\myTheta{}) d\myTheta{}.
\end{equation}
The posterior distribution is a measure of our beliefs after seeing the new
information.
\end{linenomath}

@@

%I like the example, but it may be too cute. It is also too long. I think a contrived example is good, but if there could be an example that is more relevant to model choice and comparison of inaccurate posterior distributions, I think that would be better. This is an example of empirical Bayes, but not the potential problem with the use in msbayes. Unless I am interpreting wrong. I would be careful about making it to cute as well. You may intend to make it easy to understand for a general audience, but it can also seem like talking down to Hickerson et al, who we are responding to. It just depends on how you read it.
\iffalse
This can be demonstrated with a simple, albeit contrived, example.
Let us say that principal investigator Mary and her new postdoc Will are
interested in the hypothesis that the mass of George Washington's periwig
renders the quarter dollar of the United States unfair.
That is to say their null hypothesis is that the probability of a US
quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
They can certainly evaluate this hypothesis, they can have undergraduate
worker, Joe, flip the coin for them while they tabulate the results.
But being Bayesians, before they call Joe into the lab, they agree on a
prior probability to place on the set of all possible probabilities that
the quarter will land heads when it is flipped.
Given that neither of them have a quarter, and their prior knowledge that Joe
moonlights as a magician, and is notorious for performing coin and card tricks
in the lab, they suspect there is a good chance that the quarter Joe uses will
be either two-headed or two-tailed.
So, knowing that the beta distribution is the conjugate prior for a binomial
likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
(Figure~\ref{figCoinFlip}).

@@

If Joe's flips were a representative sample, Mary and Will's empirical Bayes
estimate might very well be a better point estimate for the parameter
\myTheta{}.
However, their empirical Bayes estimate of the probability of their hypothesis
is incorrect and biased.
This simple example shows how parameter estimation is fundamentally different
from estimating the probability of a model.
While empirically informed priors can be used to obtain well-behaved parameter
estimators, using them for model choice is much less certain.
In addition to these theoretical concerns there are practical dangers to
using narrow, empirical, uniform priors for a method that has already
been shown to be biased toward models with lesser parameter space.
\fi

\subsection*{Dangers of narrow uniform priors for Bayesian model
choice} \cwlnote{}{Should this be part of the empirical Bayes section, or something else?}

\cwlnote{}{It seems like this section can be boiled down to ``empirical Bayes approaches for model choice when using uniform priors can exclude the $truth$ from the prior, which is a violation of Bayes theorem" or something like that. Picking apart what they calculated and we calculated seems like too much detail. I would try to simplify how this is being presented. This can lead into how the use of more appropriate prior distributions should be used.}
The results of \citet{Hickerson2013} reanalysis of the Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
The narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior density (HPD) interval for
the mean divergence time estimated under one of the priors used by
\citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the prior, because many of the taxon pairs
are expected to have diverged at times older than the upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
Thus, the results of \citet{Hickerson2013} indicate
Lindley's paradox is biasing the method toward models with smaller
parameter space, and as a consequence is biasing the method toward models that
exclude the truth (i.e., toward estimating model-averaged posteriors
dominated by models that exclude true values of parameters of the model).

%This should be in the section on model-averaging, not empirical Bayes limitations
We explored the propensity of the model-averaging approach of
\citet{Hickerson2013} to exclude the truth in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If Lindley's paradox causes the method to prefer models with less parameter
space, we expect \msb will preferentially sample from this incorrect model
yielding a marginal posterior that is incorrect (i.e., the model-averaged
posterior will be dominated by an incorrect model that excludes the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

\section*{Assessing the power of the model-averaging approach of
    \citet{Hickerson2013}}
\cwlnote{}{I think the empirical use of the model-averaging should go here, instead of above in the empirical Bayes section}

@@

Given our results, we conclude that the approach of
\citet{Hickerson2013} excludes regions of parameter
space containing the $truth$, and lacks power to detect random variation in
divergence times over the scale of $8\globalpopsize$ generations or more.
This roughly translates to millions of generations for mitochondrial loci, and
hundreds of millions of generations for nuclear loci.

%I would suggest removing this section
\iffalse
\section*{The power analysis of \citet{Hickerson2013}}
\citet{Hickerson2013} present a power analysis in which they find that
\msb has the power to infer multiple divergence events when divergence times
are random over hundreds of thousands of generations (rather than millions as
demonstrated by \citet{Oaks2012}).
It is not surprising that under limited parameter space the method has
increased power to detect temporal variation in divergences over narrower time
windows than millions of generations.
However, what is important to consider is whether those conditions are relevant
to real-world applications of the method.
\citet{Oaks2012} explore the behavior of the method under three divergence time
priors, as narrow as 0--5 coalescent units. This is quite narrow considering
that this expresses the prior belief that all 22 taxon pairs diverged within
this window.
\citet{Hickerson2013} limit their power analysis to a single prior of 0--1
coalescent unit.
This prior setting assumes that there is enough a priori information to
be 100\% certain that all taxa (18 for their simulations) diverged within
the last 4$\globalpopsize$ generations.
This does not seem applicable to most empirical systems.
Furthermore, even when such extensive prior information is available, to only
be able to detect multiple divergences on the scale of hundreds of thousands of
generations does not seem very powerful.

@@

Lastly, \citet{Hickerson2013} translate their results from units of
\globalcoalunit generations to generations assuming a mutation rate of
$1.92\e{-8}$ mutations per site per generation.
If we translate their results to a scale more consistent with rates of mutation
of nuclear loci ($1\e{-9}$), even under the very optimistic prior settings used
by \citet{Hickerson2013} the method can only reliably reject the extreme case
of one divergence event when divergences are random over a period of more than
3 million generations.
Again, considering \citet{Hickerson2013} are assuming prior knowledge that
all population pairs diverged within the last coalescent unit, this
does not seem particularly powerful.
\fi

%This seems to specific, not sure about including
\section*{Validation analyses}
\highLight{Not sure where to put this section}.
\highLight{This justifies presenting the unadjusted results in this paper.}
\highLight{Is it worth including just for this purpose?}
Following \citet{Oaks2012}, we characterize the model-choice behavior of the
model-averaging approach of \citet{Hickerson2013} under the ideal conditions
where the prior is correct (i.e., the data are generated from parameters drawn
from the same prior distributions used in the analysis).
We used the same prior models as above ($M_1$--$M_5$;
Table~\ref{tabModelChoiceEmpirical}), and generated 50,000 pseudo-replicate
datasets under this prior (10,000 from each model).
We used a simulated data structure of eight population pairs, with a single
1000 bp locus sampled from 10 individuals from each population.
We then analyzed each of these replicate datasets using the same prior,
retaining 1000 posterior samples.
Our results are very similar to \citet{Oaks2012}, but we note that they
are not directly comparable as our simulations contained eight population
pairs rather than 10 (Figure~\ref{figValidationMCBehavior}).
We find that the method does a decent job of estimating the posterior
probability of divergence models when all assumptions of the method
are met, the prior is correct, and the unadjusted posterior estimates
are used.
Similar to \cite{Oaks2012}, we find that the regression-adjusted estimates of
the model probabilities are biased.

@@

%This seems to nit-picky. Probably not worth including it
\section*{Other clarifications}

@@

\section*{Conclusions}
We demonstrate how the approximate Bayesian model choice method implemented in
\msb can be strongly biased away from models with greater parameter space.
We find that this is likely caused by the inappropriate
use of uniform priors on most of the model's parameters.
These priors necessitate the use of broad priors that place high prior density
in unlikely regions of parameter space, less the risk of excluding the truth
\emph{a priori}.
This likely hinders the marginal likelihoods of models with greater parameter
space, either due to more divergence time parameters or broader prior
distributions on those parameters.
We show that the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} does not mitigate this bias, but rather causes it to
manifest by sampling predominantly from models that may exclude the true values
of the parameters.
Exploring cogent prior probability distributions on most of the model's
parameters, in addition to different priors over divergence models, should
help mitigate the methods biases.

>>>>

{\sffamily
    \noindent\textbf{ABSTRACT} \\
    \noindent Recently, \citet{Oaks2012} presented a simulation-based
    assessment of the approximate Bayesian phylogeographical model choice
    method implemented in \msb, and found the method to lack robustness and
    power to detect temporal variation in divergences that are randomly
    distributed over relatively broad periods of evolutionary history.
    They conclude that a likely mechanism behind the bias toward models with
    few divergence events is the small marginal likelihoods of models with more
    divergence time parameters due to the integration over vast parameter space
    imposed by broad uniform priors characterized by low likelihood and high
    prior density.
    This phenomenon is often referred to as Lindley's paradox
    \citep{Lindley1957}.  \citet{Hickerson2013} have responded to this work,
    criticising the priors used by \citet{Oaks2012} and presenting an
    approximate Bayesian model-averaging approach that uses narrow, empirically
    informed uniform priors.
    \citet{Hickerson2013} conclude this approach circumvents the issues
    revealed by \citet{Oaks2012} and yields robust inference of divergence
    models.
    Furthermore, they argue that the biases revealed by \citet{Oaks2012} are
    inherent to the inefficient rejection algorithm implemented in \msb, rather
    than a result of Lindley's paradox.
    Here we show that the methodology of \citet{Hickerson2013} suffers from a
    fundamental error that renders some of their results invalid and the
    remainder difficult to interpret.
    Furthermore, we demonstrate how the approach of \citet{Hickerson2013} still
    suffers from a bias toward models with less parameter space, which
    manifests in a dangerously strong tendency to sample predominantly from
    models that exclude the true values of the model's parameters.
    Our results suggest that their model-averaged results are dominated by
    models that likely exclude at least some of the true divergence times
    across the 22 pairs of Philippine vertebrates, which adds to the
    difficulty in interpreting their results.
    We also show that in addition to this dangerous behavior, the approach of
    \citet{Hickerson2013} is still strongly biased toward inferring
    simultaneous divergences even when the true divergences are randomly
    distributed over millions of generations.
    Our results, coupled with those of \citet{Oaks2012}, strongly suggest that
    Lindley's paradox is a primary cause of the bias of \msb toward models with
    lesser parameter space.
    We discuss ways to mitigate this bias without resorting to adding an
    additional dimension of model choice to the model or using dangerous
    empirically informed uniform priors.

@@

%CWL:
% \highLight{The goal of this paper needs to be to highlight the major
%     differences of opinion on how ABC can be used in comparative phylogeography
%     and how these changes to msbayes can be made that will improve the
%     inference in the future. We should avoid nit-picking the Hickerson paper
%     and try to stay positive.}

@@

Regarding the mechanism behind the poor behavior of the method,
\citet{Oaks2012} suggest the primary cause is likely the low marginal
likelihoods of parameter-rich models integrated over vast parameter space with
low probability of producing the data, yet relatively high prior density
\citep[this is often referred to as Lindley's paradox;][]{Lindley1957}.
Note, this suggests the bias is extrinsic to \msb, and the numerical
approximation machinery of \msb could be sound.
\citet{Hickerson2013} suggest the bias is intrinsic to \msb, concluding the
method's rejection algorithm is inefficient and will be increasingly biased as
the overall space of the model increases, either as a function of the number of
taxon pairs or the width of the uniform priors on nuisance parameters.
\citet{Hickerson2013} support their position by giving a probabilistic argument
that focuses on only one of the three prior models used by \citet{Oaks2012}.
We show that this argument is based on an empirical Bayesian approach and
questionable assumptions, and does not explain the bias of the method found in
many of the analyses of \citet{Oaks2012}. 
Furthermore, we present results of additional analyses that, when combined
with the results of \citet{Oaks2012}, strongly suggest that Lindley's paradox
is playing a large role in the poor behavior of \msb.

@@

Regarding perspectives about mitigating the bias, \citet{Oaks2012} suggest that
alternative prior probability distributions on divergence models and nuisance
parameters could reduce the effect of Lindley's paradox.
They also layout simulation-based procedures for determining power, accuracy,
and robustness of the method given a dataset, and recommend any application of
\msb should be accompanied by such procedures, especially if any biological
conclusions are drawn from the results.
Alternatively, \citet{Hickerson2013} present an approximate Bayesian
model-averaging approach for accommodating uncertainty in selecting among
empirically guided priors, and champion the method as a means of avoiding the
pitfalls raised by \citet{Oaks2012}.
We show that fundamental errors in this approach render some of their results
invalid and leave the remaining results difficult to interpret.
Furthermore, we follow the advice of \citet{Oaks2012} and present
simulation-based assessments of Hickerson et al.'s (\citeyear{Hickerson2013})
approach.
Our results demonstrate that the model-averaging approach of
\citet{Hickerson2013} is biased and dangerous.
The approach provides another means by which the model can ``escape'' large
parameter space, and the method's bias toward smaller models remains.
This manifestation of the bias can be dangerous and often excludes the true
parameter space due to the use of narrow uniform priors.
Furthermore we discuss the potential theoretical and practical problems of
empirical Bayesian model choice, which is used and encouraged by
\citet{Hickerson2013} without discussing its potential complications.

%CWL:
%It may be important to point out the error made in their paper, but it can
%also be nit-picky, it depends on how the error impacts the overall message of
%our response.  We should strive to keep the response short and directed at the
%big picture items. If there is a way to still point out the error, then maybe
%some of this section should be used
\section*{An error in Hickerson et al.'s re-analysis of the Philippines data}
\citet{Hickerson2013} re-analyzed the dataset of \citet{Oaks2012} using a
model-averaging approach, where they placed a discrete uniform prior over eight
different prior models (see Table 1 of \citet{Hickerson2013}).
In our initial attempts to explore the behavior of this approach, we found
a fundamental error in the methodology of \citet{Hickerson2013}:
their model mixes different time units.

@@

% \cwlnote{}{This part seems important, but not related to the error in units
% discussed above}
Another important characteristic of the approach used by \citet{Hickerson2013}
that makes their results difficult to interpret in addition to this error is
their use of narrow, empirically guided uniform priors in an
approximate-Bayesian model-choice framework.
We discuss the dangers of this approach in the next section, and show how the
results of \citet{Hickerson2013} likely exclude true values of the model's
parameters.

@@

\section*{The dangers of empirical Bayesian model choice}
\citet{Hickerson2013} repeatedly refer to the prior distributions used by
\citet{Oaks2012} as ``poorly selected''. 
However, this is misleading, as \citet{Oaks2012} discuss in detail how they
selected their priors (see their section ``Specifying and simulating the joint
prior'').
They detail that the limitation in using uniform prior distributions in \msb
necessitates awkward broad priors to avoid excluding the truth, \textit{a
    priori}.
What \citet{Hickerson2013} really mean by ``poorly selected'' is that
\citet{Oaks2012} did not use their data to inform their initial prior
distributions (i.e., they did not use an empirical Bayesian approach).
\citet{Oaks2012} did use empirically informed priors when assessing both the
prior sensitivity of the method and determining the power of \msb under
real-world conditions with highly informative priors.  
\citet{Oaks2012} discuss
the potential dangers of taking an empirical Bayesian approach to model choice
(see the last paragraph of ``Assessing prior sensitivity of \msb'' in
\citet{Oaks2012}), and we expand on this here by exploring both the theoretical
and practical implications of using empirically informed priors for Bayesian
model choice.

\subsection*{Theoretical implications of empirical priors for Bayesian model
choice}
\begin{linenomath}
Bayesian inference is a rational method of inductive learning in which Bayes'
rule is used to update our beliefs about a model as new information becomes
available.
If we let \allParameterValues represent the set of all possible parameter
values, we can define a prior distribution for all $\theta \in
\allParameterValues$ such that $p(\theta)$ describes our belief that any given
\myTheta{} is the true value of the parameter.
If we let \allDatasets represent all possible datasets then we can 
define a sampling model for all $\theta \in
\allParameterValues$ and $\alignment{}{} \in \allDatasets$ such that
$p(\alignment{}{} | \theta)$ measures our belief that any dataset \alignment{}{}
will be generated by any model state \myTheta{}.
After collecting a new dataset \alignment{i}{}, we can use Bayes' rule to
calculate the posterior distribution
\begin{equation}
    p(\myTheta{} \given \alignment{i}{}) = \frac{p(\alignment{i}{} \given 
    \myTheta{})p(\myTheta{})}{p(\alignment{i}{})},
    \label{eq:bayesrule}
\end{equation}
where
\begin{equation}
    p(\alignment{i}{}) = \int_{\myTheta{}} p(\alignment{i}{} \given
    \myTheta{})p(\myTheta{}) d\myTheta{}.
\end{equation}
The posterior distribution is a measure of our beliefs after seeing the new
information.
\end{linenomath}

@@

%CWL:
%I like the example, but it may be too cute. It is also too long. I think a
%contrived example is good, but if there could be an example that is more
%relevant to model choice and comparison of inaccurate posterior distributions,
%I think that would be better. This is an example of empirical Bayes, but not
%the potential problem with the use in msbayes. Unless I am interpreting wrong.
%I would be careful about making it to cute as well. You may intend to make it
%easy to understand for a general audience, but it can also seem like talking
%down to Hickerson et al, who we are responding to. It just depends on how you
%read it.
This can be demonstrated with a simple, albeit contrived, example.
Let us say that principal investigator Mary and her new postdoc Will are
interested in the hypothesis that the mass of George Washington's periwig
renders the quarter dollar of the United States unfair.
That is to say their null hypothesis is that the probability of a US
quarter landing heads when tossed is less than 0.5 ($\theta < 0.5$).
They can certainly evaluate this hypothesis, they can have undergraduate
worker, Joe, flip the coin for them while they tabulate the results.
But being Bayesians, before they call Joe into the lab, they agree on a
prior probability to place on the set of all possible probabilities that
the quarter will land heads when it is flipped.
Given that neither of them have a quarter, and their prior knowledge that Joe
moonlights as a magician, and is notorious for performing coin and card tricks
in the lab, they suspect there is a good chance that the quarter Joe uses will
be either two-headed or two-tailed.
So, knowing that the beta distribution is the conjugate prior for a binomial
likelihood, they decide to use a $beta(a=0.5, b=0.5)$ prior distribution
(Figure~\ref{figCoinFlip}).

@@

If Joe's flips were a representative sample, Mary and Will's empirical Bayes
estimate might very well be a better point estimate for the parameter
\myTheta{}.
However, their empirical Bayes estimate of the probability of their hypothesis
is incorrect and biased.
This simple example shows how parameter estimation is fundamentally different
from estimating the probability of a model.
While empirically informed priors can be used to obtain well-behaved parameter
estimators, using them for model choice is much less certain.
In addition to these theoretical concerns there are practical dangers to
using narrow, empirical, uniform priors for a method that has already
been shown to be biased toward models with lesser parameter space.

\subsection*{Practical dangers of empirically informed uniform priors for
    Bayesian model choice}
% \cwlnote{}{Should this be part of the empirical Bayes section, or something
%     else?}

% \cwlnote{}{It seems like this section can be boiled down to ``empirical Bayes
%     approaches for model choice when using uniform priors can exclude the
%     $truth$ from the prior, which is a violation of Bayes theorem" or something
%     like that. Picking apart what they calculated and we calculated seems like
%     too much detail. I would try to simplify how this is being presented. This
%     can lead into how the use of more appropriate prior distributions should be
%     used.}
The results of Hickerson et al.'s \citeyear{Hickerson2013} reanalysis of the
Philippine dataset strongly favored models with the narrowest, empirically
informed prior on divergence time, and thus their model-averaged posterior
estimates are dominated by models $M_1$ and $M_2$ (see Table 1 of
\citet{Hickerson2013}).
This is concerning, because the narrowest \divt{} prior used by
\citet{Hickerson2013} ($\divt{} \sim U(0,0.1)$) likely excludes the true
divergence times for at least some of the Philippine taxa, a major problem when
using uniform priors.
\citet{Hickerson2013} set this prior to match the 95\% highest posterior
density (HPD) interval for the mean divergence time estimated under one of the
priors used by \citet{Oaks2012} (see Tables 2 and 3 of \citet{Oaks2012}).
Given this interval estimate is for the \emph{mean} divergence time across all
22 taxa, it may be inappropriate to set this as the prior, because many of the
taxon pairs are expected to have diverged at times older than the upper limit.
Furthermore, this prior is \emph{excluded} from the 95\% HPD interval estimates
of the mean divergence time under the other two priors explored by
\citet{Oaks2012} (under these priors the 95\% HPD is approximately 0.3--0.6;
see Table~6 of \citet{Oaks2012}).
Thus, the results of \citet{Hickerson2013} indicate Lindley's paradox is
biasing the method toward models with smaller parameter space, and as a
consequence is biasing the method toward models that exclude the truth (i.e.,
toward estimating model-averaged posteriors dominated by models that exclude
true values of parameters of the model).

%CWL:This should be in the section on model-averaging, not empirical Bayes
%limitations
We explored the propensity of the model-averaging approach of
\citet{Hickerson2013} to exclude the truth in two ways.
First, we re-analyzed the Philippines dataset using the model-averaging approach
of \citet{Hickerson2013}, but set one of prior models with a uniform prior on
divergence times that is unrealistically narrow, and almost certainly excludes
most, if not all, of the true divergence times of the 22 taxon pairs.
If Lindley's paradox causes the method to prefer models with less parameter
space, we expect \msb will preferentially sample from this incorrect model
yielding a marginal posterior that is incorrect (i.e., the model-averaged
posterior will be dominated by an incorrect model that excludes the truth).
Second, we generated simulated datasets for which the divergence times are
drawn from an exponential distribution and applied the approach of
\citet{Hickerson2013} to each of them to see how often the method excludes the
truth.

@@

\section*{Assessing the power of the model-averaging approach of
    \citet{Hickerson2013}}
% \cwlnote{}{I think the empirical use of the model-averaging should go here,
%     instead of above in the empirical Bayes section}

@@

Given our results, we conclude that the approach of \citet{Hickerson2013}
excludes regions of parameter space containing the truth, and lacks power to
detect random variation in divergence times over the scale of $8\globalpopsize$
generations or more.
This roughly translates to millions of generations for mitochondrial loci, and
hundreds of millions of generations for nuclear loci.

%CWL: I would suggest removing this section
\section*{The power analysis of \citet{Hickerson2013}}
\citet{Hickerson2013} present a power analysis in which they find that
\msb has the power to infer multiple divergence events when divergence times
are random over hundreds of thousands of generations (rather than millions as
demonstrated by \citet{Oaks2012}).
It is not surprising that under limited parameter space the method has
increased power to detect temporal variation in divergences over narrower time
windows than millions of generations.
However, what is important to consider is whether those conditions are relevant
to real-world applications of the method.
\citet{Oaks2012} explore the behavior of the method under three divergence time
priors, as narrow as 0--5 coalescent units. This is quite narrow considering
that this expresses the prior belief that all 22 taxon pairs diverged within
this window.
\citet{Hickerson2013} limit their power analysis to a single prior of 0--1
coalescent unit.
This prior setting assumes that there is enough a priori information to
be 100\% certain that all taxa (18 for their simulations) diverged within
the last 4$\globalpopsize$ generations.
This does not seem applicable to most empirical systems.
Furthermore, even when such extensive prior information is available, to only
be able to detect multiple divergences on the scale of hundreds of thousands of
generations does not seem very powerful.

@@

Lastly, \citet{Hickerson2013} translate their results from units of
\globalcoalunit generations to generations assuming a mutation rate of
$1.92\e{-8}$ mutations per site per generation.
If we translate their results to a scale more consistent with rates of mutation
of nuclear loci ($1\e{-9}$), even under the very optimistic prior settings used
by \citet{Hickerson2013} the method can only reliably reject the extreme case
of one divergence event when divergences are random over a period of more than
3 million generations.
Again, considering \citet{Hickerson2013} are assuming prior knowledge that
all population pairs diverged within the last coalescent unit, this
does not seem particularly powerful.

%CWL: This seems to specific, not sure about including
\section*{Validation analyses}
\highLight{Not sure where to put this section}.
\highLight{This justifies presenting the unadjusted results in this paper.}
\highLight{Is it worth including just for this purpose?}
Following \citet{Oaks2012}, we characterize the model-choice behavior of the
model-averaging approach of \citet{Hickerson2013} under the ideal conditions
where the prior is correct (i.e., the data are generated from parameters drawn
from the same prior distributions used in the analysis).
We used the same prior models as above ($M_1$--$M_5$;
Table~\ref{tabModelChoiceEmpirical}), and generated 50,000 pseudo-replicate
datasets under this prior (10,000 from each model).
We used a simulated data structure of eight population pairs, with a single
1000 bp locus sampled from 10 individuals from each population.
We then analyzed each of these replicate datasets using the same prior,
retaining 1000 posterior samples.
Our results are very similar to \citet{Oaks2012}, but we note that they
are not directly comparable as our simulations contained eight population
pairs rather than 10 (Figure~\ref{figValidationMCBehavior}).
We find that the method does a decent job of estimating the posterior
probability of divergence models when all assumptions of the method
are met, the prior is correct, and the unadjusted posterior estimates
are used.
Similar to \cite{Oaks2012}, we find that the regression-adjusted estimates of
the model probabilities are biased.

@@

%CWL: This seems to nit-picky. Probably not worth including it
\section*{Other clarifications}

@@

\section*{Conclusions}
We demonstrate how the approximate Bayesian model choice method implemented in
\msb can be strongly biased away from models with greater parameter space.
As suggested by \citet{Oaks2012}, this is likely caused by the inappropriate
use of uniform priors on most of the model's parameters.
These priors necessitate the use of broad priors that place high prior density
in unlikely regions of parameter space, less the risk of excluding the truth
\emph{a priori}.
This likely hinders the marginal likelihoods of models with greater parameter
space, either due to more divergence time parameters or broader prior
distributions on those parameters.
We show that the empirical Bayesian model-averaging approach of
\citet{Hickerson2013} does not mitigate this bias, but rather causes it to
manifest by sampling predominantly from models that may exclude the true values
of the parameters.
Exploring cogent prior probability distributions on most of the model's
parameters, in addition to different priors over divergence models, should
help mitigate the method's biases.
